ms2

### 2017-08-28 ms2/ms2_display.Rmd
cleanup

ineq %>%
  filter(unit_type=='state', drug_group != 'overall') %>%
  ggplot(aes(x=fnz, y=mean, color=drug_group)) +
  geom_abline(slope=1.5, color='gray') +
  geom_point() +
  xlab('Fraction nonzero') + ylab('claims per beneficiary') +
  ggtitle('Fraction consuming and mean consumption, states') +
  theme_minimal() +
  scale_color_manual(values=cbbPalette)
```

@@

```{r univariate_result_correlation}
results %>%
  filter(str_detect(model, '^uni'), term != '(Intercept)') %>%
  select(unit_type, bug, drug_group, term, estimate) %>%
  spread(term, estimate) %>%
  group_by(unit_type, drug_group) %>%
  filter(n() > 2) %>%
  do(tidy(cor(select(., -unit_type, -bug, -drug_group)))) %>%
  ungroup() %>%
  rename(x=.rownames) %>%
  gather('y', 'value', fnz:nb_mu) %>%
  filter(x > y) %>%
  mutate(key=str_c(x, '_', y)) %>%
  select(-x, -y) %>%
  spread(key, value) %>%
  kable
```

>>>>

ineq %>%
  filter(unit_type=='state', drug_group != 'overall') %>%
  ggplot(aes(x=fnz, y=mean, color=drug_group)) +
  #geom_abline(slope=1.5, color='gray') +
  stat_smooth(method='lm', se=F, fullrange=TRUE) +
  geom_point() +
  xlab('Fraction nonzero') + ylab('claims per beneficiary') +
  geom_hline(yintercept=0) + geom_vline(xintercept=0) +
  ggtitle('Fraction consuming and mean consumption, states') +
  theme_minimal() +
  scale_color_manual(values=cbbPalette)
```

@@

```{r univariate_result_correlation, eval=FALSE}
results %>%
  filter(str_detect(model, '^uni'), term != '(Intercept)') %>%
  select(unit_type, bug, drug_group, term, estimate) %>%
  spread(term, estimate) %>%
  group_by(unit_type, drug_group) %>%
  filter(n() > 2) %>%
  do(tidy(cor(select(., -unit_type, -bug, -drug_group)))) %>%
  ungroup() %>%
  rename(x=.rownames) %>%
  gather('y', 'value', fnz:nb_mu) %>%
  filter(x > y) %>%
  mutate(key=str_c(x, '_', y)) %>%
  select(-x, -y) %>%
  spread(key, value) %>%
  kable
```
